Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-07 text/supp.tex
Catch up on edits to the text
Bringing in figure changes and captions

\clearpage
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
TODO ``Chondrichtyhes'' IS A TYPO IN THE GPDD DATA\\
TODO ADD TOTAL NUMBER OF POINTS ON RIGHT COLUMN
\input{../analysis/stat-table}
\clearpage

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.8\textwidth]{../analysis/priors-gomp-base.pdf}
\caption{
  Probability density of the Bayesian priors for the Gompertz models. From left to right and then top to bottom: (1) per capita growth rate at $\log$(abundance) = $0$: $\lambda \sim \mathrm{Normal}(0, 10^2)$; (2) scale parameter of t-distribution process noise: $\sigma \sim \mathrm{Half\mhyphen Cauchy} (0, 2.5)$; (3) t-distribution degrees of freedom parameter: $\nu \sim \mathrm{Truncated\mhyphen Exponential}(0.01, \mathrm{min.} = 2)$; (4) AR1 correlation coefficient of residuals: $\phi \sim \mathrm{Truncated \mhyphen Normal}(0, 1, \mathrm{min.} = -1, \mathrm{max.} = 1)$. Not shown is $b$, the density dependence parameter: $b \sim \mathrm{Uniform}(-1, 2)$. The $\nu$ panel also shows two alternative priors: a weaker prior $\nu \sim \mathrm{Truncated\mhyphen Exponential}(0.005, \mathrm{min.} = 2)$, and a stronger prior $\nu \sim \mathrm{Truncated\mhyphen Exponential}(0.02, \mathrm{min.} = 2)$.
}
  \label{fig:priors}
\end{center}
\end{figure}

@@

% \begin{figure}[htbp]
% \begin{center}
% \includegraphics[width=\textwidth]{../analysis/sim-gompertz.pdf}
% \caption{
% TODO WILL REMOVE ALL OR MOST OF THIS
%   Simulation testing the Gompertz estimation model when the process deviation
%   draws were chosen so that $\nu$ could be estimated close to the true value
%   outside the full population model (``effective $\nu$'' within a CV of 0.2 of
%   specified $\nu$). The simulation was run across population $\nu$ values
%   (columns) and different scenarios (colours): (1) 100 time steps and no
%   observation error, (2) 50 time steps and no observation error, (3) 50 time
%   steps and observation error drawn from $\mathrm{Normal} (0, 0.2^2)$ but
%   ignored, and (4) 50 time steps with observation error in which the quantity
%   of observation error was assumed known. Dashed horizontal lines show the true
%   population values; these true values were chosen to represent approximately
%   the median values as estimated from the Global Population Dynamics Database.
%   Individual dots and lines
%   represent a stochastic draws from the true population distribution and
%   a model fitting (median and 80\% credible intervals). The panels from top to
%   bottom show $1/\nu$, process noise scale parameter $\sigma$, growth rate
%   parameter $\lambda$, and the density dependence parameter $b$.
% }
% \label{fig:sim-gompertz}
% \end{center}
% \end{figure}

@@

% \begin{figure}[htbp]
% \begin{center}
% \includegraphics[width=\textwidth]{../analysis/sim-gompertz-boxplots.pdf}
% \caption{
% TODO WILL REMOVE ALL OR MOST OF THIS
%   The distribution of median estimates from the same simulation as described in
%   Fig.~\ref{fig:sim-gompertz}. The boxes show the interquartile range. The
%   whiskers extend to $1.5$ times the interquartile range and outliers are shown
%   as dots. Note that these distributions represent the output from only 20
%   simulation iterations, so there is some level of remaining sampling noise.
% }
% \label{fig:sim-gompertz-boxplots}
% \end{center}
% \end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/check-sim-box.pdf}
\caption{
TODO WILL REMOVE ALL OR MOST OF THIS
  The probability that $\nu < 10$ (i.e.\ the approximate probability of heavy
  tails) for the same simulation scenarios as shown in
  Fig.~\ref{fig:sim-gompertz} and Fig.~\ref{fig:sim-gompertz-boxplots}. Within
  each scenario the dots represent stochastic draws from the true population
  distributions combined with model fits.
}
\label{fig:sim-prob}
\end{center}
\end{figure}

>>>>

\clearpage
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
TODO ADD TOTAL NUMBER OF POINTS ON RIGHT COLUMN
\input{../analysis/stat-table}
\clearpage

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.8\textwidth]{../analysis/priors-gomp-base.pdf}
\caption{
Probability density of the Bayesian priors for the Gompertz models. From left to right and then top to bottom: (1) per capita growth rate at $\log$(abundance) = $0$: $\lambda \sim \mathrm{Normal}(0, 10^2)$; (2) scale parameter of t-distribution process noise: $\sigma \sim \mathrm{Half\mhyphen Cauchy} (0, 2.5)$; (3) t-distribution degrees of freedom parameter: $\nu \sim \mathrm{Truncated\mhyphen Exponential}(0.01, \mathrm{min.} = 2)$; (4) AR1 correlation coefficient of residuals: $\phi \sim \mathrm{Truncated \mhyphen Normal}(0, 1, \mathrm{min.} = -1, \mathrm{max.} = 1)$. Not shown is $b$, the density dependence parameter: $b \sim \mathrm{Uniform}(-1, 2)$. The $\nu$ panel also shows two alternative priors: a weaker prior $\nu \sim \mathrm{Truncated\mhyphen Exponential}(0.005, \mathrm{min.} = 2)$, and a stronger prior $\nu \sim \mathrm{Truncated\mhyphen Exponential}(0.02, \mathrm{min.} = 2)$. The inset panel shows the same data but with a log-transformed x axis.
}
\label{fig:priors}
\end{center}
\end{figure}

@@

% \begin{figure}[htbp]
% \begin{center}
% \includegraphics[width=\textwidth]{../analysis/sim-gompertz.pdf}
% \caption{
% Simulation testing the Gompertz estimation model when the process deviation
% draws were chosen so that $\nu$ could be estimated close to the true value
% outside the full population model (``effective $\nu$'' within a CV of 0.2 of
% specified $\nu$). The simulation was run across population $\nu$ values
% (columns) and different scenarios (colours): (1) 100 time steps and no
% observation error, (2) 50 time steps and no observation error, (3) 50 time
% steps and observation error drawn from $\mathrm{Normal} (0, 0.2^2)$ but
% ignored, and (4) 50 time steps with observation error in which the quantity
% of observation error was assumed known. Dashed horizontal lines show the true
% population values; these true values were chosen to represent approximately
% the median values as estimated from the Global Population Dynamics Database.
% Individual dots and lines
% represent a stochastic draws from the true population distribution and
% a model fitting (median and 80\% credible intervals). The panels from top to
% bottom show $1/\nu$, process noise scale parameter $\sigma$, growth rate
% parameter $\lambda$, and the density dependence parameter $b$.
% }
% \label{fig:sim-gompertz}
% \end{center}
% \end{figure}

@@

% \begin{figure}[htbp]
% \begin{center}
% \includegraphics[width=\textwidth]{../analysis/sim-gompertz-boxplots.pdf}
% \caption{
%   The distribution of median estimates from the same simulation as described in
%   Fig.~\ref{fig:sim-gompertz}. The boxes show the interquartile range. The
%   whiskers extend to $1.5$ times the interquartile range and outliers are shown
%   as dots. Note that these distributions represent the output from only 20
%   simulation iterations, so there is some level of remaining sampling noise.
% }
% \label{fig:sim-gompertz-boxplots}
% \end{center}
% \end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{../analysis/check-sim-box.pdf}
\caption{
Simulation testing the Gompertz estimation model when the process deviation
draws were chosen so that $\nu$ could be estimated close to the true value
outside the full population model (``effective $\nu$'' within a CV of 0.2 of
specified $\nu$).
Plots show the probability that $\nu < 10$ (i.e.\ the approximate probability
of heavy tails) across three population $\nu$ values
(3, 5, and normal) and different scenarios panels: (1) 100 time steps and no
observation error, (2) 50 time steps and no observation error, (3) 50 time
steps and observation error drawn from $\mathrm{Normal} (0, 0.2^2)$ but
ignored, and (4) 50 time steps with observation error in which the quantity
of observation error was assumed known.
Within
each scenario the dots represent stochastic draws from the true population
distributions combined with model fits.
}
\label{fig:sim-prob}
\end{center}
\end{figure}
